Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-05-27 Multiresolution_framework/ltx/manuscript.tex
minor changes

	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\frac{\pi in\nu}{2}).\label{eq:MRA-Wavelettransform}

>>>>

	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
